### 2014-11-13 minimax.tex
Fix verbatim code.

The code in Fig.~\ref{minimax:check-end} deals with the tree expansion process.
The first three rules (lines 1-10) deal
with the case where no children nodes are created and the last three rules
(12-29) deal with the cases for that create new nodes. In particular, the two
rules in lines 12-25 generate new nodes using the
\mytt{exists} language construct, which creates a child node 
\mytt{B}. We link \mytt{B} with its parent (\mytt{parent(B, A)})
and kick start the expansion of that node \mytt{B} by adding a \mytt{play}
fact.

@@

expand(A, Board, [0 | Xs], N, P, Depth),
Depth >= 5
  -o exists B. (\underline{set-static(B)},
       \underline{set-default-priority(B, float(Depth + 1))},
       play(B, Board ++ [P | Xs], next(P), \underline{Depth + 1}),
       expand(A, Board ++ [0], Xs, N + 1, P, \underline{Depth}),
       parent(B, A)).

expand(A, Board, [0 | Xs], N, P, Depth),
Depth < 5
  -o exists B. (\underline{set-default-priority(B, float(Depth + 1))},
       play(B, Board ++ [P | Xs], next(P), \underline{Depth + 1}),
       expand(A, Board ++ [0], Xs, N + 1, P, \underline{Depth}),
       parent(B, A)).

@@

With coordination, we set the priority of a node to be its depth (lines 15 and
22) so the tree is expanded in a depth-first fashion,
leading to a memory complexity of $\mathcal{O}(d t)$, where $d$
is the depth of the tree and $t$ is the number of threads.
Since threads prioritize deeper nodes, the scores of the first leaves are immediately
computed and then sent to the parent node. At this point, the leaves are deleted
and reused for other nodes in the tree, resulting in minimal memory usage.

>>>>

The code in Fig.~\ref{minimax:check-end} deals with the tree expansion process.
The first three rules (lines 1-10) deal
with the case where no children nodes are created and the last three rules
(12-29) deal with the cases for that create new nodes. In particular, the two
rules in lines 12-26 generate new nodes using the
\mytt{exists} language construct, which creates a child node 
\mytt{B}. We link \mytt{B} with its parent (\mytt{parent(B, A)})
and kick start the expansion of that node \mytt{B} by adding a \mytt{play}
fact.

@@

expand(A, Board, [0 | Xs], N, P, \underline{Depth}),
Depth >= 5
  -o exists B. (\underline{set-static(B)},
       \underline{set-default-priority(B, float(Depth + 1))},
       play(B, Board ++ [P | Xs], next(P), \underline{Depth + 1}),
       expand(A, Board ++ [0], Xs, N + 1, P, \underline{Depth}),
       parent(B, A)).

expand(A, Board, [0 | Xs], N, P, \underline{Depth}),
Depth < 5
  -o exists B. (
       \underline{set-default-priority(B, float(Depth + 1))},
       play(B, Board ++ [P | Xs], next(P), \underline{Depth + 1}),
       expand(A, Board ++ [0], Xs, N + 1, P, \underline{Depth}),
       parent(B, A)).

@@

With coordination, we set the priority of a node to be its depth (lines 15 and
23) so the tree is expanded in a depth-first fashion,
leading to a memory complexity of $\mathcal{O}(d t)$, where $d$
is the depth of the tree and $t$ is the number of threads.
Since threads prioritize deeper nodes, the scores of the first leaves are immediately
computed and then sent to the parent node. At this point, the leaves are deleted
and reused for other nodes in the tree, resulting in minimal memory usage.

### 2014-11-13 splash-bp.tex
Fix verbatim code.

// TREE BUILDING
// expand tree by adding neighbor nodes
inactive(A), tree(A, All, Next) -o expand-tree(A, All, Next).
// start tree since we do not have one
inactive(A), *underline{@priority(A, A, P)}, P > 0.0
   -o expand-tree(A, [A], [A]).
// end tree building
expand-tree(A, All, Next), length(All) >= maxnodes
   -o first-phase(A, All, reverse(All)).
// expand tree
expand-tree(A, All, [A | Next]), length([A | Next]) < maxnodes
   -o [collect => L | Side | !edge(A, L, Side),
         0 = count(All, L), // L is not in All
         0 = count(Next, L), // L is not in Next
         *underline{@priority(A, L, P), P > 0.0,}
         *underline{@cpu-id(A, L, Id1)},
         *underline{@cpu-id(A, A, Id2), Id1 = Id2} |
         send-tree(A, All, Next ++ L)].

@@

We measured the behavior of LBP and SBP for both CLM and GraphLab.
Fig.~\ref{results:splash_bp} shows that both systems have very similar behavior
when using a variable number of threads.  The differences in performance between
GraphLab and CLM comes mainly because GraphLab performs in-place updates of
neighbor belief values, while CLM compiler and runtime system performs naive
manipulation of facts by deriving rules. The in-place update could be generated
by the compiler using smarter compilation strategies.

>>>>

// TREE BUILDING: expand tree by adding nodes
inactive(A), tree(A, All, Next)
   -o expand-tree(A, All, Next).
// start tree since we do not have one
inactive(A), *underline{@priority(A, A, P)}, P > 0.0
   -o expand-tree(A, [A], [A]).
// end tree building
expand-tree(A, All, Next), len(All) >= maxnodes
   -o first-phase(A, All, reverse(All)).
// expand tree
expand-tree(A, All, [A | Next]), len(Next) < maxnodes-1
   -o [collect => L | Side | !edge(A, L, Side),
         0 = count(All, L), // L is not in All
         0 = count(Next, L), // L is not in Next
         *underline{@priority(A, L, P), P > 0.0,}
         *underline{@cpu-id(A, L, Id1)},
         *underline{@cpu-id(A, A, Id2), Id1 = Id2} |
         send-tree(A, All, Next ++ L)].

@@

We measured the behavior of LBP and SBP for both CLM and GraphLab.
Fig.~\ref{results:splash_bp} shows that both systems have very similar behavior
when using a variable number of threads.  The differences in performance between
GraphLab and CLM comes mainly because GraphLab performs in-place updates of
neighbor belief values, while CLM compiler and runtime system perform na\"{i}ve
manipulation of facts by deriving rules. The in-place update could be generated
by the compiler using smarter compilation strategies.
